Sequence Labeling for Gait Analysis using LSTM

### 2015-05-09 paper/paper.tex
Minor fixes

\section{Data}
\label{sec:Data}
Our training and testing was conducted on data from 10 healthy subjects walking 
on a treadmill at three different speeds for 50 seconds. Each sequence of 50 seconds is called a trial. This amounts to a total of 1500 seconds of recorded data, which roughly correspond to 1000 gait cycles.  For each subject, 3D motion capture data was collected using 18 reflective markers placed at precise body locations.%
\footnote
{
    The locations used were toe, ankle, heel, knee, greater trochanter (hip), tibia, femur, and anterior and posterior superior illiac spine (pelvis) on each leg.
}
The sampling frequency of this data is 100Hz. The event labels (target) were computed from ground force reaction data from force sensors embedded in the treadmill 
which is considered the gold standard in the field. 
In order to compute events the ground reaction forces in gravity's axis are thresholded ($20 N$) and whenever they exceed this threshold, the foot is considered to be on the ground (stance). By searching for the transitions between stance and no-stance, the events are found.
The sampling frequency of this data is 1kHz.

>>>>

\section{Data}
\label{sec:Data}
Our training and testing was conducted on data from 10 healthy subjects walking 
on a treadmill at three different speeds for 50 seconds. Each sequence of 50 seconds is called a trial. This amounts to a total of 1500 seconds of recorded data, which roughly correspond to 1000 gait cycles.  For each subject, 3D motion capture data was collected using 18 reflective markers placed at precise body locations.%
\footnote
{
    The locations used were toe, ankle, heel, knee, greater trochanter (hip), tibia, femur, and anterior and posterior superior illiac spine (pelvis) on each leg.
}
The sampling frequency of this data is 100Hz. The event labels (target) were computed from ground force reaction data from force sensors embedded in the treadmill 
which is considered the gold standard in the field. 
In order to compute events the ground reaction forces in gravity's axis are thresholded at 20N; whenever the forces exceed this threshold, the foot is considered to be on the ground (stance). By searching for the transitions between stance and no-stance, the events are found.
The sampling frequency of this data is 1kHz.
